Human capital mediates natural selection in contemporary humans

### 2022-03-19 why-natural-selection.Rmd
Use shades to darken light colours

old_ggplot <- function (
        dfr, 
        fill_col, 
        n_regs, 
        ...,
        score_col = quo(term), 
        order_idx = 1, 
        fill_direction = 1,
        n_cats    = NULL,
        conf_int  = NULL
      ) {
  if (! missing(score_col)) score_col <- enquo(score_col)

  if (is.null(conf_int)) conf_int <- "conf.low" %in% names(dfr)

  confint_geom_segment <- if (conf_int) confint_geom_segment() else NULL

  dfr %>% mutate(
          !! score_col := pretty_names(!! score_col),
          !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
        ) %>% 
        rename(p = p.value) %>% 
        ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
                     fill = {{fill_col}}, ..., colour = p < 0.05/{{n_regs}})) +
          my_vline + 
          confint_geom_segment +
          pval_geom_point(fill = if(rlang::quo_is_null(fill_col)) "steelblue") +
          pval_scale() +
          my_fill_scale(n = n_cats, direction = fill_direction) +
          my_labs() +
          my_theme() +
          scale_linetype_manual(name = "", values = c("95% c.i. uncorrected" = 1))

}

@@

  if (n <= 2) {
    dots <- list(...)
    dots$direction <- NULL
    do.call(scale_colour_manual, c(list(values = fill_colors[1:n],
                                        aesthetics = aesthetics), 
                                   dots))
  } else {
    scale_color_brewer(aesthetics = aesthetics, ...)
  }
}

>>>>

@@

  if (n <= 2) {
    dots <- list(...)
    dots$direction <- NULL
    do.call(scale_colour_manual, c(list(values = fill_colors[1:n],
                                        aesthetics = aesthetics), 
                                   dots))
  } else {
    shades::lightness(scale_color_brewer(aesthetics = aesthetics, ...), 
                        shades::scalefac(0.85))
  }
}
